%% Centene Corporation
\cventry
{2019 -- Pres.}
{Centene Corporation}{Data Scientist III}
{}{}{}
\cvitem{\pin}{Creve Couer, \textsc{Mo}}

\cvitem{}{\labelitemi\hspace{2mm}
	Project: Geospatial regionalization of agricultural markets, utilizing GIS algorithms, graph analytics, and unsupervised clustering methods. These regions are currently deployed and utilized at the core of the business.
}
\cvitem{}{\labelitemi\hspace{2mm}
	Project: Agricultural pest modeling, utilizing time-series environmental data and user-submitted data from disparate sources. Constructed a unified modeling pipeline for regression and classification pest predictions. Projected increase of realized revenue of \$5M+
}
\cvitem{}{\labelitemi\hspace{2mm}
	Project: Individually managed an intern on an NLP, sequence modeling, imbalanced classification problem with 100+ classes. Now in proof-of-concept evaluation for internal usage, potentially saving $\sim$1000 man-hours.
}
\cvitem{}{\labelitemi\hspace{2mm}
	Collaborated across departments to author a unified Data Science Best Practices policy, along with rollout and training plan. Adherence bolsters the integrity and stability of data products, company-wide.
}
\cvitem{}{\labelitemi\hspace{2mm}
	Curated a set of viable data science projects from across the business and led a company-wide, two-day Hackathon. Several projects went on to impact the business, with one currently in production.
}
\cvitem{}{\labelitemi\hspace{2mm}
	Evaluated new data science platforms and compiled reports to inform leadership's decisions.
}
\cvitem{\textit{Tools}}{$\rightarrow$\hspace{2mm}
	Python, Jupyter, Scikit-Learn, Keras, Git, Docker
}
\vspace{4px}